---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lmdiag

<!-- badges: start -->
<!-- badges: end -->

The goal of lmdiag is to diagnose linear model (lm) assumptions by testing model residuals for normality using Shapiro-Wilk test, and for homogeneity using
Breusch-Pagan test.

## Installation

You can install the released version of lmdiag from [Github](https://github.com/) with:

``` r
devtools::install_github("KevinHzq/lmdiag", build_vignettes = TRUE, ref = "v0.1.1")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(lmdiag)
## basic example code
lm_model <- lm(lifeExp ~ gdpPercap, data = gapminder::gapminder)
lm_diag(lm_model)
```

## Development Explanation

  1. Create package folder locally using code:`create_package("~/lmdiag")`
  
  2. Enable Git for version control: `use_git()`
  
  3. Create script file for the lm_diag function: `use_r("lm_diag")`, and write the function (from Assignment 1). Then, insert and fill roxygen skeleton.
  
  4. Create this readme file: `use_readme_rmd()`, fill the template, and start documenting the development process.
  
  5. Load the function by `load_all`, and manually test the function using the example above. Also, check the function documentation with `?lm_diag` (edited the script file to improve the documentation after checking). 
  
  6. Check the package for errors using `check()`. Errors found as the lm_diag function uses two functions from the 'stats' package and one from the 'car' package.
  
  7. Fix the errors by importing those package: `use_package("stats")`, `use_package("car")`, and put gapminder (for testing) as suggest package: `use_package("gapminder", "suggest")`. Then check for error again. 
  
  8. Setup test file by `use_test()`, and write the test (from previous assignment) with 'testthat' package. Then `check()` for error again. 
  
  9. Edit the "DESCRIPTION" file, and set license by `use_mit_license("Kevin Hu")`. Update documentation using `document()`
  
  10. Create a vignette with `use_vignette("How-to-diagnose-lm-with-lmdiag")`, write a short demo of the package, then build the vignette by `build_vignettes()`
  
  11. Build Readme by `build_readme()`. `check()` for error again. `install()` the package and manually check the functionality and documentations once more.
  
  12. Commit the changes and push the files to github.
